### 2017-04-06 paper/evaluation.tex
added intro of rq6

\begin{itemize}
    \item \textbf{\RQF{}}
\end{itemize}

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakyness}}
\label{tab:rq6-efficiency}
\end{figure}

>>>>

\begin{itemize}
    \item \numRQF{}. \textbf{\RQF{}}
\end{itemize}

To answer \numRQF{}, we considered the top ten projects with
long-running test suites and all parallel modes (see
Section~\ref{sec:modes}). In this experiment, we run the test suites
with different parallel modes and evaluated the average time cost and
rate of failing tests. To avoid noise, we carefully selected only
subjects with nonfailing tests to avoid noise in our measurements.

\Fix{Elaborate results from efficiency}

Figure~\ref{tab:rq6-efficiency} summarizes our findings.

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

\Fix{Elaborate results about flakiness}

Figure~\ref{tab:rq6-flaky} summarizes our findings.

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakiness}}
\label{tab:rq6-flaky}
\end{figure}

\Fix{discuss trade-offs and elaborate conclusion....}
